\input{../praeambel.tex}

\title[Data Science Project: Ideas]{Data Science Project \\ \small Ideas}
\date{March 7, 2025}

\begin{document}
    \maketitle
    
    %\tableofcontents
    \frame{
        \centering
        \huge
        Die Quellen sind noch nicht up to date, morgen finden wir noch paar mehr, die man gut verwenden kann!
    }

    \section{Music}
    \begin{frame}{Music}{Spotify API, Songsterr/Ultimate-Guitar webscraping}
        \begin{itemize}[<+->]
            \item What chord-progressions repeat most frequent in songs by artist (e.g. Taylor Swift), timespan or genre?
            \item How did song length change through the years?
            \item What genres are more popular in which countries?
            \item Do song tempo and popularity correlate?
            \item Does the season influence the music people listen to?
        \end{itemize}
    \end{frame}

    \section{Kiel}
    \begin{frame}{Kiel}{Stadt Kiel Open Data, Immowelt API, Tourismusverband Schleswig-Holstein, Public GPS-traces}
        \begin{itemize}[<+->]
            \item What buslines/trains are most frequently late, and how late?
            \item Which districts have the highest density of coffee shops and/or bars?
            \item What influence did \alert{\textsc{\bfseries THE EVENT}}\footnote{Kieler Woche / Corona?} have on local retail and gastronomic sales?
            \item How do search requests about Kiel change during the \textquote{Kieler Woche} over the year?
            \item How high is the economical influence of the \textquote{Kieler Woche} on the city?
            \item How did rental costs change in different parts of Kiel?
            \item Are there patterns in the apartment listings over the seasons?
            \item Where are hotspots of GPS-activity in Kiel?
        \end{itemize}
    \end{frame}
    \section{Gaming}
    \begin{frame}{Gaming}{Steam API, Twitch API, Kaggle Gaming set}
        \begin{itemize}[<+->]
            \item Do playtime and ratings correlate?
            \item Which games have the longest active communities?
            \item How do Twitch-Streams influence the sales of games?
            \item Which factors influence the popularity of a game?\footnote{Oder auch: What makes a game popular? Also konkret bezogen zum Beispiel auf Tags, die ein Spiel ausgezeichnet bekommt/hat.}
        \end{itemize}
    \end{frame}

    \section{Gigachad-Gpt}
    \begin{frame}{Gigachad-Gpt}{OpenAi\footnote{Die API ist nicht frei verfügbar, aber wir könnten theoretisch prompts automatisch eingeben indem wir heimlich nen \textquote{virtuellen} browser steuern (aka. interactive session based webscraping) und prompts eingeben lassen. Verstößt aber eventuell gegen deren AGB.}, webscraping}
        \begin{itemize}[<+->]
            \item What are frequent prompts?
            \item How do answers change with the same prompt remade?
            \item ...\footnote{Mehr interessante Fragen}
        \end{itemize}
    \end{frame}

    \section{Supermarket}
    \begin{frame}{Supermarket}{LIDL/Rewe, etc.}
        \begin{itemize}[<+->]
            \item What are frequent itemsets?
            \item How do sales change during the year?
            \item What do people eat during different seasons?
            \item What do people buy during different holidays?
        \end{itemize}
    \end{frame}

    \section{Illnesses \& University}
    \begin{frame}{Illnesses \& University}{\footnote{Gute Quellen finden!}}
        \begin{itemize}[<+->]
            \item When do students/lecturers get ill?
            \item Do students/lecturers get ill at different times in the semester?
            \item Do students get ill during the examination period?
            \item Are students/lecturers suffering from higher stress compared to other people?
            \item What are the influences of university to the mental health of students/lecturers?
        \end{itemize}
    \end{frame}

    \section{Rich people}
    \begin{frame}{Rich people}{Webscraping, public social media APIS\footnote{konkretisieren}, }
        \begin{itemize}[<+->]
            \item At which time or day in the week do some famous billionaires post the most on social media?
            \item Which billionaires post most frequently on social media?
            \item Which billionaires fly the most?\footnote{Fun fact: Taylor Swift is a billionaire according to Forbes.}
            \item ...
        \end{itemize}
    \end{frame}

    \section{AI embeddings on images}
    \begin{frame}{AI embeddings on images}{Publicly available vector embedders of Images, own autoencoder\footnote{Falls wir genug Zeit haben solch ein Modell zu trainieren}, MNIST, 80 Million Tiny Images, etc.}
        \begin{itemize}[<+->]
            \item Do different encoders have similar variance on the same datasets?
            \item How do embeddings of different datasets behave?
            \item How performant are trained encoders on different datasets?
            \item What embeddings of one encoder form clusters across one dataset?
            \item How do clusters change during dimensionality reduction via PCA?
            \item Can we identify different clusters by eye with a 2D-PCA?\footnote{Hab das zufälligerweise gestern Abend gemacht mit den Bildern aus dem Medienpädagogik-Projekt vom dem ich erzählt hatte, war sehr interessant. Der Encoder hatte dabei 512 Dimensionen, also kann sowas auch sehr lange dauern zu berechnen.}
        \end{itemize}
    \end{frame}
\end{document}
