\input{../praeambel.tex}

\title[Data Science Project: Week 2]{Data Science Project \\ \small Week 2}
\date{March 14, 2025}

\begin{document}
    \maketitle
    
    \section{Main Question}
    \begin{frame}{Main Question {\tiny for now\dots}}
        \centering\huge
        \textquote{How do various musical elements vary in the most popular songs of the last 20 years?}
    \end{frame}
    
    \section{Aspects to analyze}
    \begin{frame}[allowframebreaks]{Aspects to analyze {\tiny for now\dots}}
        \begin{itemize}
            \item What chord-progressions repeat most frequently? \alert{Nike \& Henri}
            \item Do certain chord-progressions dominate specific genres? \alert{Mika \& Henri}
            \item What chords and chord types (minor, major, \dots) dominate / how did the amount change? \alert{Nike \& Henri}
            \item What key signatures dominate? \alert{Sena}
        \framebreak
            \item How did song\dots
                \begin{itemize}
                    \item \dots duration \alert{Sena}
                    \item \dots tempo \alert{Sena}
                    \item \dots polarity \alert{Mika}
                    \item \dots metrics on Spotify (e.g. \textit{\textquote{danceability}}) \alert{Sena}
                \end{itemize}
                \dots vary and change over the years? Do they correlate?
            \item Which words and combinations are the most frequent? \alert{Mika}
        \end{itemize}
    \end{frame}

    \section{Datasets and Apis}
    \begin{frame}{Datasets and Apis}{\itshape What we have\dots}
        \begin{itemize}
            \item \textbf{Main source:} \textquote{Hot 100 Songs} from the Billboard Year-End of 2005 up to 2024 \alert{Nike}
            \item \textbf{Refined sources using songs from the main source:}
                \begin{itemize}
                    \item Ultimate-Guitar Webscraping links for tabs \alert{Nike}
                    \item Ultimate-Guitar Webscraping tabs-links to chords \alert{Henri}
                    \item Spotify-Api for features \alert{Sena}
                    \item Last.fm API for \textquote{topTags} (genres) \alert{Mika}
                    \item azapi API \& Genius API for lyrics \alert{Mika}
                \end{itemize}
        \end{itemize}
    \end{frame}

    \section{Plans}
    \begin{frame}{Plans}{\it What we do with it\dots}
        \begin{itemize}
            \item Clean collected URLs for chords to filter out wrong results \alert{Nike}
            \item Finalize and clean chords dataset from URLs \alert{Henri}
            \item Identify main harmonies of songs by determining key signatures from chords \alert{Henri}
            \item Extract relevant metrics and lyrics from Spotify, Last.fm, azapi/Genius \alert{Sena \& Mika}
            \item Implement algorithms for the concrete data analysis \alert{Nike, Henri, Sena \& Mika}
        \end{itemize}
    \end{frame}

    \frame{\centering\huge Questions?}
\end{document}
